The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with {\em Gaia} Data and Beyond

### 2019-04-24 paper/ms.tex
Add paragraph about coordinate system errors

>>>>

Galactocentric coordinate system offsets can also be generated by errors in
the parameters of the Galactocentric coordinate system. However, such
parameters have been measured to high enough precision that they are likely
subdominant to the intrinsic variation of the midplane across large distances.
On shorter scales, they are likely the dominant source of error.
